Verifying synchronous distributed algorithms using IVy

### 2018-08-06 paper/paper.tex
- page 4, section (II.ii.2): explain the difference between upper and lower 	case placeholders in more detail

To assign values to relations, functions or variables $:=$ is used. To assign to multiple values
at the same time one can use an uppercase placeholder. For example, to set all nodes with an incoming message to \textit{failed}:

\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
failed(X) := ~incoming_message(X);
\end{lstlisting}
\end{mdframed}

@@

action fail_node_and_send(x:node) = {
  fail(x) := true;
  call send;
}
export fail_node_and_send

action send = {
  sent(X) := true;
}
\end{lstlisting}
\end{mdframed}

@@

\textit{Assume} is used to exclude the possibility of something happening.  This is mostly useful in combination with non-deterministic assignments that one wants to restrict. The following action chooses a random node to assign to y, but will not allow control to pass if the chosen node has failed. Therefore the actions will choose a random non-failed node to send a message to x.  If there is no node that hasn't failed, this action cannot terminate.

@@

Assume simplifies modelling in some situations, as it can easily eliminate impossible behaviour. However,
it is risky to use assume for the same reason: one might dismiss a valid counterexample to the specification
by assuming it cannot happen. Putting $assume\ false$ at the beginning of any action will cause all checks on it
to be positive.

>>>>

@@

action exported_action(x:node) = {
  call internal_action;
}
export exported_action

action  internal_action = {
  . . .
}
\end{lstlisting}
\end{mdframed}

To assign values to relations, functions or variables $:=$ is used.
\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
action our_action(x:node) = {
  failed(x) := true;
}
\end{lstlisting}
\end{mdframed}
Lower case tokens refer to an individual value. In the code above \textit{x} refers to the specific instance of type \textit{node} that has been passed to \textit{our\_action}. The value of the relation \textit{failed(x)} is changed to \textit{true} only for that instance of \textit{node}.

In Ivy one often wants to specify system-wide state-changes. For this reason Ivy allows iterator-free assignments involving all instances of a type. To make such an assignment one can use placeholders that are denoted by uppercase tokens. For example, to set all nodes without an incoming message to \textit{failed}:

\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
failed(X:node) := ~incoming_message(X:node);
\end{lstlisting}
\end{mdframed}

\noindent This is conceptually the same as the following pseudo-code:

\begin{mdframed}[backgroundcolor=light-gray, roundcorner=10pt,leftmargin=1, rightmargin=1, innerleftmargin=15, innertopmargin=15,innerbottommargin=15, outerlinewidth=1, linecolor=light-gray]
\begin{lstlisting}
# Pseudocode only:
foreach x of type node {
  failed(x) := ~incoming_message(x);
}
\end{lstlisting}
\end{mdframed}

The language only supports assignments where each placeholder that appears on the right hand side of an assignment is also on the left hand side.

@@

\textit{Assume} is used to exclude the possibility of something happening.  This is mostly useful in combination with non-deterministic assignments that one wants to restrict. The following action chooses a random node to assign to \textit{y}, but will not allow control to pass if the chosen node has failed. Therefore the actions will choose a random non-failed node to send a message to x.  If there is no node that hasn't failed, this action cannot terminate.

@@

\textit{Assume} simplifies modelling in some situations, as it can easily eliminate impossible behaviour. However,
it is risky to use \textit{assume} for the same reason: one might dismiss a valid counterexample to the specification
by assuming it cannot happen. To give an extreme example, putting $assume\ false$ at the beginning of an exported action will cause all of Ivy's checks for induction to come out positive.
